msuRACiFits_fits_rice

### 2025-06-04 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Updated fitting script

```{r}
for (i in seq_along(datasets)) { 
  mean_temps[i] <- mean(datasets[[i]]$Tleaf) 
  mean_press[i] <- mean(datasets[[i]]$Press) }
```

@@

```{r}
Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
Gstars_rice_25<-msuRACiFit::calcGammaStar(13.7,24.6,25,21) #rice c and dHa 
```

@@

```{r}
Gstars_Pa_rice<-Gstars_rice*(1000 / 1000000)*mean_press 
```

@@

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press
```

@@

## Save parameter outputs:

@@

## Produce data tables using parameters fitted for each curve and the SSR assoaciated with each fit:

@@

>>>>

```{r}
for (i in seq_along(datasets)) { 
  mean_temps[i] <- mean(datasets[[i]]$Tleaf) 
  mean_press[i] <- mean(datasets[[i]]$Press)
  sem_mean_temps <- sd(mean_temps) / sqrt(length(mean_temps))
  sem_mean_press <- sd(mean_press) / sqrt(length(mean_press))
}
```

@@

```{r}
Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
sem_Gstars_rice<- sd(Gstars_rice)/ sqrt(length(Gstars_rice))
Gstars_rice_25<-msuRACiFit::calcGammaStar(13.7,24.6,25,21) #rice c and dHa 
```

@@

```{r}
Gstars_Pa_rice<-Gstars_rice*(1000 / 1000000)*mean_press 
sem_Gstars_Pa_rice<- sd(Gstars_Pa_rice)/ sqrt(length(Gstars_Pa_rice))
```

@@

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press
mean_Kc<-mean(all_param$Kc)
mean_Ko<-mean(all_param$Ko)
mean_Kcair<-mean(all_param$Kcair)

sem_Kc <- sd(all_param$Kc)/ sqrt(length(all_param$Kc))
sem_Ko <- sd(all_param$Ko)/ sqrt(length(all_param$Ko))
sem_Kcair <- sd(all_param$Kcair)/ sqrt(length(all_param$Kcair))
```

@@

### Save parameter outputs:

@@

## Produce data tables using parameters fitted for each curve and the SSR associated with each fit:

@@

## Compute mean and SEM of parameter values:

```{r}
VcMax <- mean(combined_results$VcMax)
J <- mean(combined_results$J)
TPU <- mean(combined_results$TPU)
Rd <-  mean(combined_results$rL)
gm <-  mean(combined_results$gm)
sem_VcMax <- sd(combined_results$VcMax)/ sqrt(length(combined_results$VcMax))
sem_J <- sd(combined_results$J)/ sqrt(length(combined_results$J))  
sem_TPU <- sd(combined_results$TPU)/ sqrt(length(combined_results$TPU)) 
sem_Rd <- sd(combined_results$rL)/ sqrt(length(combined_results$rL))
sem_gm <- sd(combined_results$gm)/ sqrt(length(combined_results$gm))   
```
